### 2018-11-19 zst/data/鲁营霖-reference.tex
add thesis

\begin{thebibliography}{0}
\bibitem{math-machine1} 吴文俊. 吴文俊论数学机械化[M]. 北京: 山东教育出版社, 1996.
\bibitem{math-machine2} 吴文俊. 数学机械化[M]. 北京: 科学出版社, 2003.
\bibitem{math-machine3} 吴文俊. 几何定理机器证明的基本原理[M]. 北京: 科学出版社, 1984.

\bibitem{LiYS} 李翊神. 孤子与可积系统[M]. 上海: 上海科技教育出版社, 1999: 1-8
\bibitem{Lsd2013} 刘适达, 刘式适. 大气学科在与物理学科的交融中发展[J]. 物理, 2013, 9
\bibitem{GuoYC} 郭玉翠. 非线性偏微分方程引论. 北京: 清华大学出版社, 2008: 127-174
\bibitem{LiuSD} 刘式适, 刘适达. 物理学中的非线性方程. 第二版. 北京: 北京大学出版社, 2012: 58-83, 222-230

\bibitem{ChongJS2010} 种劲松, 欧阳越, 李飞, 朱敏慧. 合成孔径雷达图像海洋内波探测[M]. 北京: 海洋出版社, 2010: 21-33
\bibitem{GaoST2013} 高守亭, 刘璐, 李娜. 近几年中尺度动力学研究进展[J]. 大气科学, 2013, 37(2): 319-330
\bibitem{LvJ2011} 吕君, 赵正予, 周晨. 次声波在非均匀运动大气中非线性传播特性的研究[J]. 物理学报,  2011, 60(10): 104301
\bibitem{LS1987} Uccellini L. W., Koch S. E. The Synoptic Setting and Possible Energy Sources for Mesoscale Wave Distribution[J]. Monthly Weather Review, 1987, 115(3): 721-729
\bibitem{YueFL2013} 岳甫璐, 王春明, 王慧鹏. 重力波对``7.21" 北京大暴雨过程的影响研究[C]. 创新驱动发展提高气象灾害防御能力―― 第30届中国气象学会年会, 2013
\bibitem{FangXH2005} 方欣华,杜涛. 海洋内波基础和中国海内波[M]. 青岛: 中国海洋大学出版社, 2005
\bibitem{YangBJ} 杨伯君, 赵玉芳. 高等数学物理方法[M]. 北京: 北京邮电大学出版社, 2003
%\bibitem{WangML} 王明亮. 非线性发展方程与孤立子[M]. 兰州: 兰州大学出版社, 1990
\bibitem{HuangJN} 黄景宁, 徐济仲, 熊吟涛. 孤子概念, 原理和应用[M]. 北京: 高等教育出版社, 2004: 11-17
%\bibitem{GuoBL} 郭柏灵, 苏凤秋. 孤立子[M]. 沈阳: 辽宁教育出版社, 1997
\bibitem{AblowitzClarkson} Ablowitz M. J., Clarkson P. A. Soliton, Nonlinear Evolution Equations and Inverse Scattering [M]. New York: Cambridge University Press, 1991
\bibitem{Scott1973}  Scott A. C. The Soliton: A New Concept in Applied Science[J]. Proceedings of the IEEE, 1973,  61(10): 1443-1483
\bibitem{LiuSD1982} 刘式达, 刘式适. 大气中的非线性椭圆余弦波和孤立波[J]. 中国科学B, 1982, 4
\bibitem{Grim2007}  Grimshaw R. H., Pelinovsky E., Talipova T. Modelling Internal Solitary Waves in the Coastal Ocean[J].  Surveys in Geophysics, 2007,  28: 273-298
\bibitem{ChengYL2008} 程友良, 吴英杰. 有限深分层流体中高阶内孤立波的演化方程[C]. 第二十一届全国水动力学研讨会暨第八届全国水动力学学术会议,  2008: 144-150
\bibitem{ZhangYP2014} Zhang Y. P., Nie X. X., Wei G. M., Liu R. P. The N-soliton Solution of Extended Korteweg-de Vries Equation and SAR Image Simulation of Internal Solitary Wave Propagation[J]. The  European  Physical  Journal  Applied  Physics,  online, DOI: http://dx.doi.org/ 10.1051/epjap/2014130358,  2013
\bibitem{HW2010}  Helfrich K. R., White B. L. A Model for Large-amplitude Internal Solitary Waves with Trapped Cores[J]. Nonlinear Processes in Geophysics, 2010, 17(4): 303-318
%\bibitem{LiuZL2014} 柳正来. 基于形式演算的非线性方程性质研究[D]:[硕士学位论文]. 北京: 北京航空航天大学, 2014
\bibitem{ChenWL2014} Chen W. L., Dai C. Q., Zhao L. H. Nonautonomous Superposed Akhmediev Breather in Water Waves[J]. Computers Fluids, 2014, 92: 1-6

\bibitem{AGK2014} Alias A., Grimshaw R. H., Khusnutdinova K. R. Coupled Ostrovsky Equations for Internal Waves with a Background Shear Flow[J]. Procedia IUTAM, 2014, 11: 3-14
\bibitem{PHA2013} Polina R., Houria T., Anjan B.  Perturbation of Dispersive Shallow Water Waves[J]. Ocean Engineering, 2013, 63: 1-7
\bibitem{HDA2013}Houria T., Daniela M., Anjan B. Solitary Waves and Shock Waves of the KdV6 Equation[J]. Ocean Engineering, 2013, 73: 119-125
\bibitem{Wazwaz2013} Wazwaz A. M. Multiple Soliton Solutions and Rational Solutions for the (2+1)-Dimensional Dispersive Long Water-wave System[J]. Ocean Engineering, 2013, 60: 95-98
\bibitem{LiQ2008} 李群. 陆架陆坡区内孤立波的演化: 理论分析与数值实验研究[D]:[博士学位论文]. 中国海洋大学, 2008
\bibitem{CM2008} Conte R., Musette M. The Painlev\'{e} Handbook[M]. New York: Springer, 2008
\bibitem{WeissPP} Weiss J. The Painlev\'{e} Property for Partial Differential Equations. II: B\"{a}cklund Transformation, Lax Pairs, and the Schwarzian Derivative[J]. Journal of Mathematical Physics, 1983, 24: 1405-1413
\bibitem {WeiDoctor} 魏光美. 非线性力学中三类变系数模型的 Painlev\'{e} 性质与孤子型解研究[D]:[博士学位论文]. 北京: 北京航空航天大学, 2007
\bibitem{ChenDY} 陈登远. 孤子引论[M]. 北京: 科学出版社, 2006
\bibitem{Hirota2004} Hirota R. The Direct Method in Soliton Theory[M]. London: Cambridge University Press, 2004%===Hirota
\bibitem{LouSY2006} 楼森岳, 唐晓艳. 非线性数学物理方法[M]. 北京: 科学出版社, 2006
\bibitem{Bluman2002} Bluman G. W., Anco S. C. Symmetry and Integration Methods for Differential Equations[M]. Springer, New York, 2002: 297-349
\bibitem{Olver1993} Olver P. J. Applications of Lie Groups to Differential Equations[M]. Springer, New York, 1993: 199-206

\bibitem{LiZB} 李志斌. 非线性数学物理方程的行波解[M]. 北京: 科学出版社, 2007
\bibitem{SY2010} Song M., Yang C. X, Zhang B. G. Exact Solitary Wave Solutions of the  Kadomtsov-Petviashvili-Benjamin-Bona-Mahony Equation[J]. Applied Mathematics and Computation, 2010, 217(4): 1334-1339
\bibitem{GuCH2005} 谷超豪, 胡和生, 周子翔. 孤立子理论中的达布变换及其几何应用[M]. 上海: 上海科学技术出版社, 2005
%\bibitem{WhyHxb2008} 王红艳, 胡星标. 带自相容源孤立子方程[M]. 北京: 清华大学出版社, 2008
%\bibitem{GuoBL2008} 郭柏灵, 田立新, 杨灵娥, 殷朝阳. Camassa-Holm 方程[M]. 北京: 科学出版社, 2008
%\bibitem{FanEG2004} 范恩贵. 可积系统与计算机代数[M]. 北京: 科学出版社, 2004

@@

\bibitem{Liu1988} Liu A. K. Analysis of Nonlinear Internal Waves in the New York Bight[J]. Journal of Geophysical Research, 1988, 93: 12317-12329
\bibitem{Duda2004}Duda T. F., Lynch J. F., Irish J. D., et al. Internal Tide and Nonlinear Wave Behavior in the Continental Slope in the Northern South China Sea[J]. Ocean Engineering, 2004, 29: 1105-1131 %====ISW,In-Situ.

@@

\bibitem{eKdV90} Marchant T. R., Smyth N. F. The Extended Korteweg-de Vries Equation and the Resonant Flow of a Fluid Over Topography[J]. Journal of Fluid Mechanics, 1990, 221: 263-288%=======eKdV []???
\bibitem{SW2012} El-Tantawy S. A., Moslem W. M. Nonlinear Electrostatic Excitations in Electron-depleted Electronegative Dusty Plasma with Two-negative Ion Species[J]. Astrophysics and Space Science, 2012, 337: 209-215
\bibitem{Grim99} Grimshaw R., Pelinovsky E., Talipova T. Solitary Wave Transformation in a Medium with Sign-variable Quadratic Nonlinearity and Cubic Nonlinearity[J]. Journal of Physics D, 1999, 132: 40-62

@@

\bibitem{HM2006} Helfrich K. R., Melville W. K. Long Nonlinear Internal Waves[J]. Annual Review of Fluid Mechanics, 2006, 38: 395-425%======eKdV,ISW.
\bibitem{OS1989} Ostrovsky L. A., Stepanyants Y. A. Do Internal Solitions Exist in the Ocean?[J]. Reviews of Geophysics, 1989, 27: 293-310%====eKdV,ISW
\bibitem{Grim04} Grimshaw R., Pelinovsky E., Talipova T., and Kurkin A. Simulation of the Transformation of Internal Solitary Waves on Oceanic Shelves[J]. Journal of Physical Oceanography, 2004, 34: 2774-2779%=====ScS???

@@

\bibitem{Lj07} Li J., Xu T., Meng X. H., et al. Lax Pair, B\"{a}cklund Transformation and N-soliton-like Solution for a Variable-coefficient Gardner Equation from Nonlinear Lattice, Plasma Physics and Ocean Dynamics with Symbolic Computation[J]. Journal of Mathematical Analysis and Applications, 2007, 336: 1443-1455%=====v-eKdV.
    \bibitem{Lyp13} Liu Y. P., Gao Y. T., Wei G. M. Integrable Aspects and Soliton Interaction for a Generalized Inhomogeneous Gardner Model with External Force in Plasmas and Fluids[J]. Physical Review E, 2013, 88: 053204 %======v-eKdV,
    \bibitem{Liuy2011} Liu Y., Gao Y. T., Sun Z. Y., et al. Multi-soliton Solutions of the Forced Variable-coefficient Extended Korteweg–de Vries Equation Arisen in Fluid Dynamics of Internal Solitary Waves[J]. Nonlinear Dynamics, 2011, 66: 575-587
    \bibitem{Wazwaz07} Wazwaz A. M. New Solitons and Kink Solutions for the Gardner Equation[J]. Communications in Nonlinear Science and Numerical Simulation, 2007, 12: 1395-1404
    \bibitem{Chow08} Shek E. C. M., Chow K. W. The Discrete Modified Korteweg-de Vries Equation with Non-vanishing Boundary Conditions: Interactions of Solitons[J]. Chaos, Solitons and Fractals, 2008, 36: 296-302

@@

%========NLS
\bibitem{Tb2012} Lv X., Tian B. Novel Behavior and Properties for the Nonlinear Pulse Propagation in Optical Fibers[J]. The  European  Physical  Journal  Applied  Physics, 2012, 97: 10005
\bibitem{YG2003} Kivshar Y. G., Agrawal P. Optical Solitons: From Fibers to Photonic crystals[M]. Academic Press, 2003
\bibitem{Tb2005} Tian B., Shan W. R., Zhang C. Y., et al. Schr\"{o}dinger Model from Plasma Physics, Arterial Mechanics and Optical Fibers with Symbolic Computation[J]. The European Physical Journal, 2005, B(47): 329-332
\bibitem{JJ2000} L\'{o}pez J.L., Soler J. Asymptotic Behaviour to the 3D Schr\"{o}dinger/Hartree-Poisson and Wigner-Poisson Systems[J]. Mathematical Methods in the Applied Sciences, 2000, 10: 923-943
\bibitem{RG1993} Fedele R., Miele G., Palumbo L., et al. Thermal Wave Model for Nonlinear Longitudinal Dynamics in Particle Accelerators[J]. Physics Letters A, 1993, 173: 407-413
\bibitem{GB2007} Dong G., Hu B. Management of Bose-Einstein Condensates by a Spatially Periodic Modulation of the Atomic S-wave Scattering Length[J]. Physical Review A,  2007, 75: 013625
\bibitem{KH2008} Dysthe K., Krogstad H. E., M\"{u}ller P. Oceanic Rogue Waves[J]. Annual Review of Fluid Mechanics, 2008, 40: 287-310
\bibitem{CG2012} Dai C. Q., Zhou G. Q., Zhang J. F. Controllable Optical Rogue Waves in the Femtosecond Regime[J]. Physical Review E, 2012, 85: 016603

\bibitem{RL2005} Yang R.C., Li L., Hao R.Y., et al. Combined Solitary Wave Solutions for the Inhomogeneous Higher-order Nonlinear Schr\"{o}dinger Equation[J]. Physical Review E, 2005, 71: 036616
\bibitem{RL2004} Hao R. Y., Li L., Li Z. H., et al. Exact Multisoliton Solutions of the Higher-order Nonlinear Schr\"{o}dinger Equation with Variable Coefficients[J]. Physical Review E, 2004, 70: 066603
\bibitem{JQC2005} Zhang J. F., Yang Q., Dai C. Q. Optical Quasi-soliton Solutions for Higher-order Nonlinear Schr\"{o}dinger Equation with Variable Coefficients[J]. Optics Communications, 2005, 248: 257–265
\bibitem{KAV2007} Porsezian K., Hasegawa A., Serkin V. N., et al. Ganapathy, Dispersion and Nonlinear Management for Femtosecond Optical Solitons[J]. Physical Review A, 2007, 361: 504
\bibitem{JL2006} Wang J. F., Li L., Li Z. H., et al. Generation, Compression and Propagation of Pulse Trains under Higher-order Effects[J]. Optics Communications, 2006, 263: 328
\bibitem{RLM12} Ma R. L. Study on the Propagation Model for the Deep-sea Internal Waves and Its Numerical Simulation[D]:[博士学位论文], 中国海洋大学, 山东, 2012
\bibitem{AJ2010} Ankiewicz A., Soto-Crespo J. M., Akhmediev N. Rogue Waves and Rational Solutions of the Hirota Equation[J]. Physical Review E, 2010, 81: 046602
\bibitem{HZ2013} Zhao H. Q., Zhu Z. N. Solitons and Dynamic Properties of the Coupled Semidiscrete Hirota Equation[J]. AIP Advances, 2013, 3: 022111
%\bibitem{Yzy2014} Yu F. J., Yan Z. Y. New Rogue Waves and Dark-bright Soliton Solutions for a Coupled Nonlinear Schr\"{o}dinger Equation with Variable Coefficients[J]. Applied Mathematics and Computation, 2014, 233: 351-358

%Painleve 分析
\bibitem {ARS1} Ablowitz M. J., Ramani A., Segur H. A Connection between Nonlinear Evolution Equation and Ordinary Differential Equaiton of P-type. I[J]. Journal of Mathematical Physics, 1980, 21(4): 715-721
\bibitem {ARS2} Ablowitz M. J., Ramani A., Segur H. A Connection between Nonlinear Evolution Equation and Ordinary Differential Equaiton of P-type. II[J]. Journal of Mathematical Physics, 1980, 21(5): 1006-1015
\bibitem{WeissBT} Weiss J. The Painlev\'{e} Property and B\"{a}cklund Transformations for the Sequence of Boussinesq Equations[J]. Journal of Mathematical Physics, 1985, 26: 258-268
\bibitem{KRS2011} Singh K., Gupta R. K., Kumar S. Benjamin-Bona-Mahony (BBM) Equation with Variable Coefficients: Similarity Reductions and Painlev\'{e} Analysis[J]. Applied Mathematics and Computation, 2011, 217: 7021-7027

@@

%======             CK                  ===================
\bibitem{CK1989} Clarkson P. A., Kruskal M. D. New Similarity Reductions for Boussinesq Equation[J]. Journal of Mathematical Physics, 1989, 30: 2201-2217;
   Clarkson  P. A. New Similarity Solutions for the Modified Boussinesq Equation[J]. Journal of Physics A, 1989, 22: 2355-2367
\bibitem{Lyq2010} Liang Y. Q., Wei G. M., Li X. N. Painlev\'{e} Integrability, Similarity Reductions, New Soliton and Soliton-like Similarity Solutions for the (2+1)-Dimensional BKP Equation[J]. Nonlinear Dynamics, 2010, 62: 195-202%====CK

>>>>

\begin{thebibliography}{0}
\bibitem{LiYS} 李翊神. 孤子与可积系统[M]. 上海: 上海科技教育出版社, 1999: 1-8
\bibitem{Lsd2013} 刘适达, 刘式适. 大气学科在与物理学科的交融中发展[J]. 物理, 2013, 9
\bibitem{GuoYC} 郭玉翠. 非线性偏微分方程引论. 北京: 清华大学出版社; 2008: 127-174
\bibitem{LiuSD} 刘式适, 刘适达. 物理学中的非线性方程. 第二版. 北京: 北京大学出版社; 2012: 58-83, 222-230

\bibitem{ChongJS2010} 种劲松, 欧阳越, 李飞, 朱敏慧. 合成孔径雷达图像海洋内波探测[M]. 北京: 海洋出版社, 2010: 21-33
\bibitem{GaoST2013} 高守亭, 刘璐, 李娜. 近几年中尺度动力学研究进展[J]. 大气科学, 2013, 37(2): 319-330
\bibitem{LvJ2011} 吕君, 赵正予, 周晨. 次声波在非均匀运动大气中非线性传播特性的研究[J]. 物理学报,  2011, 60(10):104301
\bibitem{LS1987} Uccellini L. W., Koch S. E. The Synoptic Setting and Possible Energy Sources for Mesoscale Wave Distribution[J]. Monthly Weather Review, 1987, 115(3): 721-729
\bibitem{YueFL2013} 岳甫璐, 王春明, 王慧鹏. 重力波对``7.21" 北京大暴雨过程的影响研究[C]. 创新驱动发展提高气象灾害防御能力―― 第30届中国气象学会年会, 2013
\bibitem{FangXH2005} 方欣华,杜涛. 海洋内波基础和中国海内波[M]. 青岛: 中国海洋大学出版社, 2005
\bibitem{YangBJ} 杨伯君, 赵玉芳. 高等数学物理方法[M]. 北京: 北京邮电大学出版社, 2003
\bibitem{WangML} 王明亮. 非线性发展方程与孤立子[M]. 兰州: 兰州大学出版社, 1990
\bibitem{HuangJN} 黄景宁, 徐济仲, 熊吟涛. 孤子概念, 原理和应用[M]. 北京: 高等教育出版社, 2004: 11-17
\bibitem{GuoBL} 郭柏灵, 苏凤秋. 孤立子[M]. 沈阳: 辽宁教育出版社, 1997
\bibitem{AblowitzClarkson} Ablowitz M. J., Clarkson P. A. Soliton, Nonlinear Evolution Equations and Inverse Scattering [M]. New York: Cambridge University Press, 1991
\bibitem{Scott1973}  Scott A. C. The Soliton: A New Concept in Applied Science[J]. Proceedings of the IEEE, 1973,  61(10): 1443-1483
\bibitem{LiuSD1982} 刘式达, 刘式适. 大气中的非线性椭圆余弦波和孤立波[J]. 中国科学B, 1982, 4
\bibitem{Grim2007}  Grimshaw R. H., Pelinovsky E., Talipova T. Modelling Internal Solitary Waves in the Coastal Ocean[J].  Surveys in Geophysics, 2007,  28: 273-298
\bibitem{ChengYL2008} 程友良, 吴英杰. 有限深分层流体中高阶内孤立波的演化方程[C]. 第二十一届全国水动力学研讨会暨第八届全国水动力学学术会议,  2008: 144-150
\bibitem{ZhangYP2014} Zhang Y. P., Nie X. X., Wei G. M., Liu R. P. The N-soliton Solution of Extended Korteweg-de Vries Equation and SAR Image Simulation of Internal Solitary Wave Propagation[J]. The  European  Physical  Journal  Applied  Physics,  online, DOI: http://dx.doi.org/ 10.1051/epjap/2014130358,  2013
\bibitem{HW2010}  Helfrich K. R., White B. L. A Model for Large-amplitude Internal Solitary Waves with Trapped Cores[J]. Nonlinear Processes in Geophysics, 2010, 17(4): 303-318
\bibitem{LiuZL2014} 柳正来. 基于形式演算的非线性方程性质研究[D]:[硕士学位论文]. 北京: 北京航空航天大学, 2014
\bibitem{ChenWL2014} Chen W. L., Dai C. Q., Zhao L. H. Nonautonomous Superposed Akhmediev Breather in Water Waves[J]. Computers Fluids, 2014, 92:1-6

\bibitem{AGK2014} Alias A., Grimshaw R. H., Khusnutdinova K. R. Coupled Ostrovsky Equations for Internal Waves with a Background Shear Flow[J]. Procedia IUTAM, 2014, 11:3-14
\bibitem{PHA2013} Polina R., Houria T., Anjan B.  Perturbation of Dispersive Shallow Water Waves[J]. Ocean Engineering, 2013, 63:1-7
\bibitem{HDA2013}Houria T., Daniela M., Anjan B. Solitary Waves and Shock Waves of the KdV6 Equation[J]. Ocean Engineering, 2013, 73:119-125
\bibitem{Wazwaz2013} Wazwaz A. M. Multiple Soliton Solutions and Rational Solutions for the (2+1)-dimensional Dispersive Long Water-wave System[J]. Ocean Engineering, 2013, 60: 95-98
\bibitem{LiQ2008} 李群. 陆架陆坡区内孤立波的演化: 理论分析与数值实验研究[D]:[博士学位论文]. 中国海洋大学, 2008
\bibitem{CM2008} Conte R., Musette M. The Painlev\'{e} Handbook[M]. New York: Springer, 2008
\bibitem{WeissPP} Weiss J. The Painlev\'{e} property for partial differential equations. II: B\"{a}cklund transformation, Lax pairs, and the Schwarzian derivative [J]. Journal of Mathematical Physics, 1983, 24:1405-1413
\bibitem {WeiDoctor} 魏光美. 非线性力学中三类变系数模型的 Painlev\'{e} 性质与孤子型解研究[D]:[博士学位论文]. 北京: 北京航空航天大学, 2007
\bibitem{ChenDY} 陈登远. 孤子引论[M]. 北京: 科学出版社, 2006
\bibitem{Hirota2004} Hirota R. The direct method in soliton theory[M]. London: Cambridge University Press, 2004%===Hirota
\bibitem{LouSY2006} 楼森岳, 唐晓艳. 非线性数学物理方法[M]. 北京: 科学出版社, 2006
\bibitem{Bluman2002} Bluman G. W., Anco S. C. Symmetry and Integration Methods for Differential Equations[M]. Springer, New York, 2002: 297-349
\bibitem{Olver1993} Olver P. J. Applications of Lie Groups to Differential Equations[M]. Springer, New York, 1993: 199-206

\bibitem{LiZB} 李志斌. 非线性数学物理方程的行波解[M]. 北京: 科学出版社, 2007
\bibitem{SY2010} Song M., Yang C. X, Zhang B. G. Exact Solitary Wave Solutions of the  Kadomtsov-Petviashvili-Benjamin-Bona-Mahony Equation[J]. Applied Mathematics and Computation, 2010, 217(4): 1334-1339
\bibitem{GuCH2005} 谷超豪, 胡和生, 周子翔. 孤立子理论中的达布变换及其几何应用[M]. 上海:上海科学技术出版社, 2005
\bibitem{WhyHxb2008} 王红艳, 胡星标. 带自相容源孤立子方程[M].北京: 清华大学出版社, 2008
%\bibitem{GuoBL2008} 郭柏灵, 田立新, 杨灵娥, 殷朝阳. Camassa-Holm 方程[M]. 北京: 科学出版社, 2008
\bibitem{FanEG2004} 范恩贵. 可积系统与计算机代数[M]. 北京: 科学出版社, 2004

@@

\bibitem{Liu1988} Liu A. K. Analysis of Nonlinear Internal Waves in the New York Bight[J]. Journal of Geophysical Research, 1988, 93:12317-12329
\bibitem{Duda2004}Duda T. F., Lynch J. F., Irish J. D., et al. Internal Tide and Nonlinear Wave Behavior in the Continental Slope in the Northern South China Sea[J]. Ocean Engineering, 2004, 29:1105-1131 %====ISW,In-Situ.

@@

\bibitem{eKdV90} Marchant T. R., Smyth N. F. The Extended Korteweg-de Vries Equation and the Resonant Flow of a Fluid Over Topography[J]. Journal of Fluid Mechanics, 1990, 221:263-288%=======eKdV []???
\bibitem{SW2012} El-Tantawy S. A., Moslem W. M. Nonlinear Electrostatic Excitations in Electron-depleted Electronegative Dusty Plasma with Two-negative Ion species[J]. Astrophysics and Space Science, 2012, 337:209-215
\bibitem{Grim99} Grimshaw R., Pelinovsky E., Talipova T. Solitary Wave Transformation in a Medium with Sign-variable Quadratic Nonlinearity and Cubic Nonlinearity[J]. Journal of Physics D, 1999, 132:40-62

@@

\bibitem{HM2006} Helfrich K. R., Melville W. K. Long Nonlinear Internal Waves[J]. Annual Review of Fluid Mechanics, 2006, 38:395-425%======eKdV,ISW.
\bibitem{OS1989} Ostrovsky L. A., Stepanyants Y. A. Do Internal Solitions Exist in the Ocean?[J]. Reviews of Geophysics, 1989, 27:293-310%====eKdV,ISW
\bibitem{Grim04} Grimshaw R., Pelinovsky E., Talipova T., and Kurkin A. Simulation of the Transformation of Internal Solitary Waves on Oceanic Shelves[J]. Journal of Physical Oceanography, 2004, 34:2774-2779%=====ScS???

@@

\bibitem{Lj07} Li J., Xu T., Meng X. H., et al. Lax Pair, B\"{a}cklund Transformation and N-soliton-like Solution for a Variable-coefficient Gardner Equation from Nonlinear Lattice, Plasma Physics and Ocean Dynamics with Symbolic Computation[J]. Journal of Mathematical Analysis and Applications, 2007, 336:1443-1455%=====v-eKdV.
    \bibitem{Lyp13} Liu Y. P., Gao Y. T., Wei G. M. Integrable Aspects and Soliton Interaction for a Generalized Inhomogeneous Gardner Model with External Force in Plasmas and Fluids[J]. Physical Review E, 2013, 88:053204 %======v-eKdV,
    \bibitem{Liuy2011} Liu Y., Gao Y. T., Sun Z. Y., et al. Multi-soliton Solutions of the Forced Variable-coefficient Extended Korteweg–de Vries Equation Arisen in Fluid Dynamics of Internal Solitary Waves[J]. Nonlinear Dynamics, 2011, 66:575-587
    \bibitem{Wazwaz07} Wazwaz A. M. New Solitons and Kink Solutions for the Gardner Equation[J]. Communications in Nonlinear Science and Numerical Simulation, 2007, 12:1395-1404
    \bibitem{Chow08} Shek E. C. M., Chow K. W. The Discrete Modified Korteweg-de Vries Equation with Non-vanishing Boundary Conditions: Interactions of Solitons[J]. Chaos, Solitons and Fractals, 2008, 36:296-302

@@

%========NLS
\bibitem{Tb2012} Lv X., Tian B. Novel Behavior and Properties for the Nonlinear Pulse Propagation in Optical Fibers[J]. The  European  Physical  Journal  Applied  Physics, 2012, 97: 10005
\bibitem{YG2003} Kivshar Y. G., Agrawal P. Optical Solitons: From Fibers to Photonic crystals[M]. Academic Press, 2003
\bibitem{Tb2005} Tian B., Shan W. R., Zhang C. Y., et al. Schr\"{o}dinger Model from Plasma Physics, Arterial Mechanics and Optical Fibers with Symbolic computation[J]. The European Physical Journal, 2005, B(47): 329-332
\bibitem{JJ2000} L\'{o}pez J.L., Soler J. Asymptotic Behaviour to the 3D Schr\"{o}dinger/Hartree-Poisson and Wigner-Poisson Systems[J]. Mathematical Methods in the Applied Sciences, 2000, 10: 923-943
\bibitem{RG1993} Fedele R., Miele G., Palumbo L., et al. Thermal Wave Model for Nonlinear Longitudinal Dynamics in Particle Accelerators[J]. Physics Letters A, 1993, 173: 407-413
\bibitem{GB2007} Dong G., Hu B. Management of Bose-Einstein Condensates by a Spatially Periodic Modulation of the Atomic S-wave Scattering Length[J]. Physical Review A,  2007, 75: 013625
\bibitem{KH2008} Dysthe K., Krogstad H. E., M\"{u}ller P. Oceanic Rogue Waves[J]. Annual Review of Fluid Mechanics, 2008, 40: 287-310
\bibitem{CG2012} Dai C. Q., Zhou G. Q., Zhang J. F. Controllable Optical Rogue Waves in the Femtosecond Regime[J]. Physical Review E, 2012, 85: 016603

\bibitem{RL2005} Yang R.C., Li L., Hao R.Y., et al. Combined Solitary Wave Solutions for the Inhomogeneous Higher-order Nonlinear Schr\"{o}dinger Equation[J]. Physical Review E, 2005, 71: 036616
\bibitem{RL2004} Hao R. Y., Li L., Li Z. H., et al. Exact Multisoliton Solutions of the Higher-order Nonlinear Schr\"{o}dinger Equation with Variable Coefficients[J]. Physical Review E, 2004, 70: 066603
\bibitem{JQC2005} Zhang J. F., Yang Q., Dai C. Q. Optical Quasi-soliton Solutions for Higher-order Nonlinear Schr\"{o}dinger Equation with Variable Coefficients[J]. Optics Communications, 2005, 248: 257–265
\bibitem{KAV2007} Porsezian K., Hasegawa A., Serkin V. N., et al. Ganapathy, Dispersion and Nonlinear Management for Femtosecond Optical Solitons[J]. Physical Review A, 2007, 361: 504
\bibitem{JL2006} Wang J. F., Li L., Li Z. H., et al. Generation, Compression and Propagation of Pulse Trains under Higher-order Effects[J]. Optics Communications, 2006, 263: 328
\bibitem{RLM12} Ma R. L. Study on the Propagation Model for the Deep-sea Internal Waves and Its Numerical Simulation[D]:[博士学位论文], 中国海洋大学, 山东, 2012
\bibitem{AJ2010} Ankiewicz A., Soto-Crespo J. M., Akhmediev N. Rogue Waves and Rational Solutions of the Hirota Equation[J]. Physical Review E, 2010, 81: 046602
\bibitem{HZ2013} Zhao H. Q., Zhu Z. N. Solitons and Dynamic Properties of the Coupled Semidiscrete Hirota Equation[J]. AIP Advances, 2013, 3: 022111
\bibitem{Yzy2014} Yu F. J., Yan Z. Y. New Rogue Waves and Dark-bright Soliton Solutions for a Coupled Nonlinear Schr\"{o}dinger Equation with Variable Coefficients[J]. Applied Mathematics and Computation, 2014, 233: 351-358

%Painleve 分析
\bibitem {ARS1} Ablowitz M. J., Ramani A., Segur H. A Connection between Nonlinear Evolution Equation and Ordinary Differential Equaiton of P-type. I[J]. Journal of Mathematical Physics, 1980, 21(4): 715-721
\bibitem {ARS2} Ablowitz M. J., Ramani A., Segur H. A Connection between Nonlinear Evolution Equation and Ordinary Differential Equaiton of P-type. II[J]. Journal of Mathematical Physics, 1980, 21(5): 1006-1015
\bibitem{WeissBT} Weiss J. The Painlev\'{e} Property and B\"{a}cklund Transformations for the Sequence of Boussinesq Equations[J]. Journal of Mathematical Physics, 1985, 26:258-268
\bibitem{KRS2011} Singh K., Gupta R. K., Kumar S. Benjamin-Bona-Mahony (BBM) Equation with Variable Coefficients: Similarity Reductions and Painlev\'{e} Analysis[J]. Applied Mathematics and Computation, 2011, 217: 7021-7027

@@

%======             CK                  ===================
\bibitem{CK1989} Clarkson P. A., Kruskal M. D. New Similarity Reductions for Boussinesq Equation[J]. Journal of Mathematical Physics, 1989, 30: 2201-2217;
   Clarkson  P. A. New Similarity Solutions for the Modified Boussinesq Equation[J]. Journal of Physics A, 1989, 22: 2355-2367
\bibitem{Lyq2010} Liang Y. Q., Wei G. M., Li X. N. Painlev\'{e} Integrability, Similarity Reductions, New Soliton and Soliton-like Similarity Solutions for the (2+1)-dimensional BKP Equation[J]. Nonlinear Dynamics, 2010, 62: 195-202%====CK
